### 2018-09-11 cover-letter/cover-letter.tex
final cover letter edits

Please find enclosed a manuscript entitled: ``Modeling and Simulation of Online
Reprocessing in the Thorium-Fuelled Molten Salt Breeder Reactor'' which Mr. 
Andrei Rykhlevskii and I are submitting for exclusive consideration of 
publication as a research article in Annals of Nuclear Energy.

>>>>

Please find enclosed a manuscript entitled: ``Modeling and Simulation of Online
Reprocessing in the Thorium-Fueled Molten Salt Breeder Reactor'' which I and my 
coauthors (Mr. Andrei Rykhlevskii and Mr. Jin Whan Bae) are submitting for 
exclusive consideration of publication as a research article in Annals of 
Nuclear Energy.
